%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Engineer Intern, Dating Ranking ENG} % Job title
    {Meta (Facebook)} % Organization
    {New York, NY} % Location
    {May 2022 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Refactored candidate retrieval for developer efficiency and scalability, reduced latency 35\%, shipped to millions of users with A/B test}
        \item {Injecting new feature to candidate ranking to improve match quality and enable experimentation opportunities}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern, Guardian Moderation Queue} % Job title
    {Spectrum Labs} % Organization
    {San Francisco, CA} % Location
    {Jan. 2022 - May 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented role-based access control}
        \item {Developed two internal features that improved efficiency and scalability}
        \item {Implemented quality of life features which saved users up to 10 minutes per moderation session}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern, Cloud Gaming Infra} % Job title
    {Facebook} % Organization
    {Menlo Park, CA} % Location
    {Jun. 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Full-stack development of video-based analysis tool; findings from tool resulted in driving engagement up 10\% on third party developer's game}
        \item {Tuned parameterization for scripts involving computer vision and clustering}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Data Structures Tutor} % Job title
    {NYU Courant Institute of Mathematical Sciences} % Organization
    {New York, NY} % Location
    {Sep. 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tutored students 10 hours/week in Data Structures (Java), assist with homework \& test preparation}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data \& AI Intern} % Job title
    {Social27 Inc.} % Organization
    {Redmond, WA} % Location
    {May 2020 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented latent feature matrix factorization ML model to address data sparsity in recommender system}
        \item {Revamped client data reports by writing Python script to scrape, clean, and visualize livestream metrics}
        \item {Owned coordination between three companies to produce 3000+ attendee virtual event as PM+CSM}
      \end{cvitems}
    }

%---------------------------------------------------------
%   \cventry
%     {UX Research/Consulting Intern} % Job title
%     {Floop Edu} % Organization
%     {Seattle, WA} % Location
%     {Dec. 2019 - Feb. 2020} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Conducted UX research vital to 2020 launch, resulting in acquisition of ~8500 (+231\%) users in a quarter}
%       \end{cvitems}
%     }

\end{cventries}